---
title: "Parameter generation"
output: html_notebook
---

This notebook generates the parameters/loads them in from CSV files
```{r}
library('MASS')

testing=TRUE

newchoices=1 #set to 1 to generate new participant choices
participant_multiplier=5 #set to 10 to have ten times the participants in the original study, etc
if (testing==TRUE) participant_multiplier=1
plotting=FALSE

source('N:/Alex/metaRL/scripts/simulate_RL.R')
```


We use 10 times the number of participants in the original paper.
```{r}
# this part of the script simulates data from the Chase et al. 2009 paper

npat_Chase=18*participant_multiplier #number of participants in Chase paper * multiplier (defined at top)
ncon_Chase=17*participant_multiplier #ditto
nsub_Chase=npat_Chase+ncon_Chase #total subs

Chase_data<-read.csv('N:/Alex/metaRL/data_from_papers/Chase_data.csv')
Chase_pat<-Chase_data[Chase_data$Group==2&Chase_data$pass.fail.exclude==1&Chase_data$other.exclude==1,]
Chase_con<-Chase_data[Chase_data$Group==1&Chase_data$pass.fail.exclude==1&Chase_data$other.exclude==1,]

#nb: 6 controls and 5 patients quit task or did not reach criterion

#probably going to ignore the test phase as not learning but PIT
#positive learning rate for patients in training phase
Chase_awin_pat <- Chase_pat$LRateP

#positive learning rate for controls in training phase
Chase_awin_con <- Chase_con$LRateP

#negative learning rate for patients in training phase
Chase_aloss_pat <- Chase_pat$LRateN

#negative learning rate for controls in training phase
Chase_aloss_con <- Chase_con$LRateN

#exploration/exploitation (essentially beta) for patients in training phase
Chase_beta_pat <- Chase_pat$Beta

#exploration/exploitation (essentially beta) for controls in training phase
Chase_beta_con <- Chase_con$Beta

Chase_params<-cbind(c(Chase_awin_pat,Chase_awin_con),c(Chase_aloss_pat,Chase_aloss_con),c(Chase_beta_pat,Chase_beta_con)) #patients then controls
save(Chase_params,file='N:/Alex/metaRL/simulated_data/Chase_params')

```
And generate data from the Kumar 2018 paper. 

```{r}
npat_Kumar=25*participant_multiplier #number of participants in Kumar paper * multiplier (defined at top)
ncon_Kumar=26*participant_multiplier #ditto
nsub_Kumar=npat_Kumar+ncon_Kumar #total subs for paper

Kumar_data<-read.csv('N:/Alex/metaRL/data_from_papers/for_Alex_Pike.csv')
Kumar_pat<-Kumar_data[grep('D',Kumar_data$X),]
Kumar_con<-Kumar_data[grep('C',Kumar_data$X),]

#positive learning rate for patients 
Kumar_awin_pat <- Kumar_pat$Alpha_Avg_Rew

#negative learning rate for patients
Kumar_aloss_pat <- Kumar_pat$Alpha_Avg_Pun

#positive beta for patients 
Kumar_betawin_pat <- Kumar_pat$Beta_Avg_Rew

#negative beta for patients
Kumar_betaloss_pat <- Kumar_pat$Beta_Avg_Pun


#positive learning rate for controls 
Kumar_awin_con <- Kumar_con$Alpha_Avg_Rew

#negative learning rate for controls
Kumar_aloss_con <- Kumar_con$Alpha_Avg_Pun

#positive beta for controls 
Kumar_betawin_con <- Kumar_con$Beta_Avg_Rew

#negative beta for controls
Kumar_betaloss_con <- Kumar_con$Beta_Avg_Pun

Kumar_params<-cbind(c(Kumar_awin_pat,Kumar_awin_con),c(Kumar_aloss_pat,Kumar_aloss_con),c(Kumar_betawin_pat,Kumar_betawin_con),c(Kumar_betaloss_pat,Kumar_betaloss_con))
save(Kumar_params,file='N:/Alex/metaRL/simulated_data/Kumar_params')
```

And load in data from Moutoussis 2018 paper
```{r}
npat_Mout=39*participant_multiplier #number of participants in Kumar paper * multiplier (defined at top)
ncon_Mout=22*participant_multiplier #ditto
nsub_Mout=npat_Mout+ncon_Mout #total subs for paper

Mout_data<-read.csv('N:/Alex/metaRL/data_from_papers/pone.0201451.s003.csv')

#learning rate for patients 
Mout_alpha_pat <- Mout_data$lrnRate.tog[Mout_data$pt_ID>100]

#learning rate for controls
Mout_alpha_con <- Mout_data$lrnRate.tog[Mout_data$pt_ID<100]

#appetitive beta for patients
Mout_winsens_pat <- Mout_data$bet_Appet.tog[Mout_data$pt_ID>100]

#appetitive beta for controls
Mout_winsens_con <- Mout_data$bet_Appet.tog[Mout_data$pt_ID<100]

#aversive beta for patients
Mout_losssens_pat <- Mout_data$bet_Aver.tog[Mout_data$pt_ID>100]

#aversive beta for controls
Mout_losssens_con <- Mout_data$bet_Aver.tog[Mout_data$pt_ID<100]

#Pavlovian bias patients
Mout_pav_pat <- Mout_data$PavBias.tog[Mout_data$pt_ID>100]

#Pavlovian bias for controls
Mout_pav_con <- Mout_data$PavBias.tog[Mout_data$pt_ID<100]

#Go bias patients
Mout_go_pat <- Mout_data$GoBias.tog[Mout_data$pt_ID>100]

#Go bias for controls
Mout_go_con <- Mout_data$GoBias.tog[Mout_data$pt_ID<100]

#lapse rate for patients
Mout_lapse_pat <- Mout_data$irNoiseXi.tog[Mout_data$pt_ID>100]

#lapse rate for controls
Mout_lapse_con <- Mout_data$irNoiseXi.tog[Mout_data$pt_ID<100]


Mout_params<-cbind(c(Mout_alpha_pat,Mout_alpha_con),c(Mout_winsens_pat,Mout_winsens_con),c(Mout_losssens_pat,Mout_losssens_con),c(Mout_pav_pat,Mout_pav_con),c(Mout_lapse_pat,Mout_lapse_con),c(Mout_go_pat,Mout_go_con)) #put go last as not used in stan models atm
save(Mout_params,file='N:/Alex/metaRL/simulated_data/Mout_params')
```

And add in data from Brown 2018 paper. Betas were estimated separately beforehand and model run with the mean. 'Since inverse temperature and reward sensitivity may not be uniquely identifiable in the RL model, inverse temperature was first estimated in a model without reward sensitivity. The RL model with reward sensitivity was then estimated with inverse temperature fixed at the group mean rather than estimated as a free parameter (similar to [Pessiglione et al., 2006]). '
```{r}
npat_Brown=39*participant_multiplier #number of participants in paper * multiplier (defined at top) #PTSD
ncon_Brown=29*participant_multiplier #ditto
nsub_Brown=npat_Brown+ncon_Brown #total subs for paper


#learning rate for patients 
Brown_alphawin_pat <- simulate_RL (n = npat_Brown, est_m = 0.10, est_sd = 0.02*sqrt(npat_Brown), plotting, min0=TRUE)
Brown_alphaloss_pat <- simulate_RL (n = npat_Brown, est_m = 0.672, est_sd = 0.011*sqrt(npat_Brown), plotting, min0=TRUE)

#learning rate for controls 
Brown_alphawin_con <- simulate_RL (n = ncon_Brown, est_m = 0.10, est_sd = 0.02*sqrt(ncon_Brown), plotting, min0=TRUE)
Brown_alphaloss_con <- simulate_RL (n = ncon_Brown, est_m = 0.708, est_sd = 0.02*sqrt(ncon_Brown), plotting, min0=TRUE)

#associability weight for patients
Brown_asso_pat <- simulate_RL (n = npat_Brown, est_m = 0.54, est_sd = 0.039*sqrt(npat_Brown), plotting, min0=TRUE)
Brown_asso_pat <-ifelse(Brown_asso_pat>1,1,Brown_asso_pat)

#associability weight for controls
Brown_asso_con <- simulate_RL (n = ncon_Brown, est_m = 0.246, est_sd = 0.033*sqrt(ncon_Brown), plotting, min0=TRUE)
Brown_asso_con <- ifelse(Brown_asso_con>1,1,Brown_asso_con)

#reward sensitivity patients
Brown_rewsens_pat <- simulate_RL (n = npat_Brown, est_m = 3.18, est_sd = 0.09*sqrt(npat_Brown), plotting, min0=TRUE)
Brown_losssens_pat <- simulate_RL (n = npat_Brown, est_m = 1.06, est_sd = 0.069*sqrt(npat_Brown), plotting, min0=TRUE)

#reward sensitivity controls
Brown_rewsens_con <- simulate_RL (n = ncon_Brown, est_m = 3.01, est_sd = 0.09*sqrt(ncon_Brown), plotting,min0=TRUE)
Brown_losssens_con <- simulate_RL (n = ncon_Brown, est_m = 1.06, est_sd = 0.065*sqrt(ncon_Brown), plotting,min0=TRUE)


#decay of unchosen pats
Brown_rewdecay_pat <- simulate_RL (n = npat_Brown, est_m = 0.89, est_sd = 0.01*sqrt(npat_Brown), plotting, min0=TRUE)
Brown_rewdecay_pat <-ifelse(Brown_rewdecay_pat>1,1,Brown_rewdecay_pat)
Brown_pundecay_pat <- simulate_RL (n = npat_Brown, est_m = 0.883, est_sd = 0.01*sqrt(npat_Brown), plotting, min0=TRUE)
Brown_pundecay_pat <-ifelse(Brown_pundecay_pat>1,1,Brown_pundecay_pat)

#decay of unchosen cons
Brown_rewdecay_con <- simulate_RL (n = ncon_Brown, est_m = 0.82, est_sd = 0.01*sqrt(ncon_Brown), plotting, min0=TRUE)
Brown_rewdecay_con <-ifelse(Brown_rewdecay_con>1,1,Brown_rewdecay_con)
Brown_pundecay_con <- simulate_RL (n = ncon_Brown, est_m = 0.857, est_sd = 0.022*sqrt(ncon_Brown), plotting, min0=TRUE)
Brown_pundecay_con <-ifelse(Brown_pundecay_con>1,1,Brown_pundecay_con)

#beta pat
Brown_rewbeta_pat <- rep(7.20, npat_Brown)
Brown_punbeta_pat <- rep(5.05, npat_Brown)

#beta con
Brown_rewbeta_con <- rep(6.35, ncon_Brown)
Brown_punbeta_con <- rep(4.35, ncon_Brown)


Brown_params<-cbind(c(Brown_alphawin_pat,Brown_alphawin_con),c(Brown_alphaloss_pat,Brown_alphaloss_con),c(Brown_asso_pat,Brown_asso_con),c(Brown_rewsens_pat,Brown_rewsens_con),c(Brown_losssens_pat,Brown_losssens_con),c(Brown_rewdecay_pat,Brown_rewdecay_con),c(Brown_pundecay_pat,Brown_pundecay_con),c(Brown_rewbeta_pat,Brown_rewbeta_con),c(Brown_punbeta_pat,Brown_punbeta_con))
save(Brown_params,file='N:/Alex/metaRL/simulated_data/Brown_params')
```

And load in data from Mkrtchian 2017 paper
```{r}
#nb S refers to 'safe' not threat here
npat_Mk=43*participant_multiplier #number of participants in Kumar paper * multiplier (defined at top)
ncon_Mk=58*participant_multiplier #ditto
nsub_Mk=npat_Mk+ncon_Mk #total subs for paper

Mk_data<-read.csv('N:/Alex/metaRL/data_from_papers/Anahit_data.csv')

#win learning rate for patients 
Mk_winalpha_pat <- Mk_data$SLRRewAlpha[Mk_data$Subject>200]

#win learning rate for controls
Mk_winalpha_con <- Mk_data$SLRRewAlpha[Mk_data$Subject<200]

#loss learning rate for patients 
Mk_lossalpha_pat <- Mk_data$SLRPunAlpha[Mk_data$Subject>200]

#loss learning rate for controls
Mk_lossalpha_con <- Mk_data$SLRPunAlpha[Mk_data$Subject<200]

#appetitive beta for patients
Mk_winsens_pat <- Mk_data$SRewBeta[Mk_data$Subject>200]

#appetitive beta for controls
Mk_winsens_con <- Mk_data$SRewBeta[Mk_data$Subject<200]

#aversive beta for patients
Mk_losssens_pat <- Mk_data$SPunBeta[Mk_data$Subject>200]

#aversive beta for controls
Mk_losssens_con <- Mk_data$SPunBeta[Mk_data$Subject<200]

#win Pavlovian bias patients
Mk_winpav_pat <- Mk_data$SRewPavEpsi[Mk_data$Subject>200]

#win Pavlovian bias for controls
Mk_winpav_con <- Mk_data$SRewPavEpsi[Mk_data$Subject<200]

#loss Pavlovian bias patients
Mk_losspav_pat <- Mk_data$SPunPavEpsi[Mk_data$Subject>200]

#loss Pavlovian bias for controls
Mk_losspav_con <- Mk_data$SPunPavEpsi[Mk_data$Subject<200]

#Go bias patients
Mk_go_pat <- Mk_data$SActionBias[Mk_data$Subject>200]

#Go bias for controls
Mk_go_con <- Mk_data$SActionBias[Mk_data$Subject<200]

#lapse rate for patients
Mk_lapse_pat <- Mk_data$SNoiseg[Mk_data$Subject>200]

#lapse rate for controls
Mk_lapse_con <- Mk_data$SNoiseg[Mk_data$Subject<200]


Mk_params<-cbind(c(Mk_winalpha_pat,Mk_winalpha_con),c(Mk_lossalpha_pat,Mk_lossalpha_con),c(Mk_winsens_pat,Mk_winsens_con),c(Mk_losssens_pat,Mk_losssens_con),c(Mk_winpav_pat,Mk_winpav_con),c(Mk_losspav_pat,Mk_losspav_con),c(Mk_go_pat,Mk_go_con),c(Mk_lapse_pat,Mk_lapse_con))
save(Mk_params,file='N:/Alex/metaRL/simulated_data/Mk_params')
```


And load in data from Aylward 2019 paper
```{r}
#nb S refers to 'safe' not threat here
npat_Ayl=44*participant_multiplier #number of participants in Kumar paper * multiplier (defined at top)
ncon_Ayl=88*participant_multiplier #ditto
nsub_Ayl=npat_Ayl+ncon_Ayl #total subs for paper

Aylward_data<-read.csv('N:/Alex/metaRL/data_from_papers/AllDataJasp.csv')

#win learning rate for patients 
Ayl_winalpha_pat <- Aylward_data$Rew_LR[Aylward_data$Diagnosis=='A']

#win learning rate for controls
Ayl_winalpha_con <- Aylward_data$Rew_LR[Aylward_data$Diagnosis=='H']

#loss learning rate for patients 
Ayl_lossalpha_pat <- Aylward_data$Punish_LR[Aylward_data$Diagnosis=='A']

#loss learning rate for controls
Ayl_lossalpha_con <- Aylward_data$Punish_LR[Aylward_data$Diagnosis=='H']

#reward sensitivity for patients
Ayl_winsens_pat <- Aylward_data$Rew_Sens[Aylward_data$Diagnosis=='A']

#reward sensitivity for controls
Ayl_winsens_con <- Aylward_data$Rew_Sens[Aylward_data$Diagnosis=='H']

#loss sensitivity for patients
Ayl_losssens_pat <- Aylward_data$Punish_Sens[Aylward_data$Diagnosis=='A']

#loss sensitivity for controls
Ayl_losssens_con <-Aylward_data$Punish_Sens[Aylward_data$Diagnosis=='H']

#lapse rate for patients
Ayl_lapse_pat <- Aylward_data$Lapse[Aylward_data$Diagnosis=='A']

#lapse rate for controls
Ayl_lapse_con <- Aylward_data$Lapse[Aylward_data$Diagnosis=='H']


Ayl_params<-cbind(c(Ayl_winalpha_pat,Ayl_winalpha_con),c(Ayl_lossalpha_pat,Ayl_lossalpha_con),c(Ayl_winsens_pat,Ayl_winsens_con),c(Ayl_losssens_pat,Ayl_losssens_con),c(Ayl_lapse_pat,Ayl_lapse_con))
save(Ayl_params,file='N:/Alex/metaRL/simulated_data/Ayl_params')
```
And the parameters from the Dombrovski paper (using samples 1 and 2, exp 1 for each)

```{r}
npat_Dom=(26+30+54+26+24+33)*participant_multiplier #number of participants in paper * multiplier (defined at top) #PTSD
ncon_Dom=(28+33)*participant_multiplier #ditto
nsub_Dom=npat_Dom+ncon_Dom #total subs for paper


#learning rate for patients 
Dom_alphawin_pat <- c(simulate_RL (n = 26, est_m = -0.8, est_sd = 1.4, plotting, min0=FALSE),
                      simulate_RL (n = 30, est_m = -0.6, est_sd = 1.6, plotting, min0=FALSE),
                      simulate_RL (n = 54, est_m = -1.2, est_sd = 1.4, plotting, min0=FALSE),
                      simulate_RL (n = 26, est_m = -0.5, est_sd = 1.7, plotting, min0=FALSE),
                      simulate_RL (n = 24, est_m = -0.3, est_sd = 1.2, plotting, min0=FALSE),
                      simulate_RL (n = 33, est_m = -0.7, est_sd = 1.3, plotting, min0=FALSE))
Dom_alphaloss_pat <- c(simulate_RL (n = 26, est_m = -0.8, est_sd = 2.1, plotting, min0=FALSE),
                      simulate_RL (n = 30, est_m = -0.6, est_sd = 2.3, plotting, min0=FALSE),
                      simulate_RL (n = 54, est_m = -1.2, est_sd = 2.2, plotting, min0=FALSE),
                      simulate_RL (n = 26, est_m = 0.1, est_sd = 2.0, plotting, min0=FALSE),
                      simulate_RL (n = 24, est_m = -0.4, est_sd = 2.1, plotting, min0=FALSE),
                      simulate_RL (n = 33, est_m = -0.3, est_sd = 2.8, plotting, min0=FALSE))

#learning rate for controls 
Dom_alphawin_con <- c(simulate_RL (n = 28, est_m = -0.8, est_sd = 1.5, plotting, min0=FALSE),
                      simulate_RL (n = 33, est_m = -0.3, est_sd = 1.4, plotting, min0=FALSE))
Dom_alphaloss_con <- c(simulate_RL (n = 28, est_m = -0.2, est_sd = 2.8, plotting, min0=FALSE),
                      simulate_RL (n = 33, est_m = -0.3, est_sd = 2.8, plotting, min0=FALSE))

#sigmoid transform for all learning rates
library('boot')
Dom_alphawin_pat<-inv.logit(Dom_alphawin_pat)
Dom_alphawin_con<-inv.logit(Dom_alphawin_con)
Dom_alphaloss_pat<-inv.logit(Dom_alphaloss_pat)
Dom_alphaloss_con<-inv.logit(Dom_alphaloss_con)

#decay weights
Dom_decay_pat <- c(simulate_RL (n = 26, est_m = -0.1, est_sd = 1.5, plotting, min0=FALSE),
                      simulate_RL (n = 30, est_m = 0.2, est_sd = 1.7, plotting, min0=FALSE),
                      simulate_RL (n = 54, est_m = 0.7, est_sd = 1.7, plotting, min0=FALSE),
                      simulate_RL (n = 26, est_m = 0.4, est_sd = 1.6, plotting, min0=FALSE),
                      simulate_RL (n = 24, est_m = 0.6, est_sd = 1.9, plotting, min0=FALSE),
                      simulate_RL (n = 33, est_m = 0.7, est_sd = 1.6, plotting, min0=FALSE))

Dom_decay_con <-c(simulate_RL (n = 28, est_m = 0.5, est_sd = 1.6, plotting, min0=FALSE),
                      simulate_RL (n = 33, est_m = 0.7, est_sd = 1.7, plotting, min0=FALSE))

Dom_decay_pat<-inv.logit(Dom_decay_pat)
Dom_decay_con<-inv.logit(Dom_decay_con)

#beta pat
Dom_beta_pat <- c(simulate_RL (n = 26, est_m = -1.5, est_sd = 0.8, plotting, min0=FALSE),
                      simulate_RL (n = 30, est_m = -1.5, est_sd = 0.8, plotting, min0=FALSE),
                      simulate_RL (n = 54, est_m = -1.3, est_sd = 0.9, plotting, min0=FALSE),
                      simulate_RL (n = 26, est_m = -1.4, est_sd = 0.9, plotting, min0=FALSE),
                      simulate_RL (n = 24, est_m = -1.6, est_sd = 0.8, plotting, min0=FALSE),
                      simulate_RL (n = 33, est_m = -1.5, est_sd = 0.6, plotting, min0=FALSE))

#beta con
Dom_beta_con <- c(simulate_RL (n = 28, est_m = -1.8, est_sd = 0.7, plotting, min0=FALSE),
                      simulate_RL (n = 33, est_m = -1.7, est_sd = 0.8, plotting, min0=FALSE))

#betas undergo an exponential transform
Dom_beta_pat<-exp(Dom_beta_pat)
Dom_beta_con<-exp(Dom_beta_con)



Dom_params<-cbind(c(Dom_alphawin_pat,Dom_alphawin_con),c(Dom_alphaloss_pat,Dom_alphaloss_con),c(Dom_decay_pat,Dom_decay_con),c(Dom_beta_pat,Dom_beta_con))
save(Dom_params,file='N:/Alex/metaRL/simulated_data/Dom_params')
```

And add in data from Liu 2017 paper
```{r}
npat_Liu=21*participant_multiplier #number of participants in paper * multiplier (defined at top) #PTSD
ncon_Liu=17*participant_multiplier #ditto
nsub_Liu=npat_Liu+ncon_Liu #total subs for paper


#learning rate
Liu_alpha_pat <- simulate_RL (n = npat_Liu, est_m = 0.21, est_sd = 0.15, plotting, min0=TRUE)
Liu_alpha_con <- simulate_RL (n = ncon_Liu, est_m = 0.31, est_sd = 0.28, plotting, min0=TRUE)

#temperature
Liu_beta_pat <- simulate_RL (n = npat_Liu, est_m = 0.31, est_sd = 0.21, plotting, min0=TRUE)
Liu_beta_con <- simulate_RL (n = ncon_Liu, est_m = 0.24, est_sd = 0.16, plotting, min0=TRUE)


Liu_params<-cbind(c(Liu_alpha_pat,Liu_alpha_con),c(Liu_beta_pat,Liu_beta_con))
save(Liu_params,file='N:/Alex/metaRL/simulated_data/Liu_params')
```

And add in data from  Blanco 2013 (Naive RL model) 
```{r}
npat_Blanco=38*participant_multiplier #number of participants in paper * multiplier (defined at top) #PTSD
ncon_Blanco=95*participant_multiplier #ditto
nsub_Blanco=npat_Blanco+ncon_Blanco #total subs for paper


#learning rate for patients 
Blanco_beta_pat <- simulate_RL (n = npat_Blanco, est_m = 0.118, est_sd = 0.044, plotting, min0=TRUE)
Blanco_beta_con <- simulate_RL (n = ncon_Blanco, est_m = 0.144, est_sd = 0.030, plotting, min0=TRUE)


Blanco_params<-cbind(c(Blanco_beta_pat,Blanco_beta_con))
save(Blanco_params,file='N:/Alex/metaRL/simulated_data/Blanco_params')
```
Add in parameters from Millner 2018 (using single prior as they found that fit best)
```{r}
npat_Mill=85*participant_multiplier #number of participants in paper * multiplier (defined at top) #PTSD
ncon_Mill=44*participant_multiplier #ditto
nsub_Mill=npat_Mill+ncon_Mill #total subs for paper


#nondecision time T
Mill_T_pat <- simulate_RL (n = npat_Mill, est_m = 0.02, est_sd = 0.15, plotting, min0=TRUE) #-0.2 to 0.5 
#but pWiener won't work unless this is greater than 0 - this doesn't really matter anyway
Mill_T_con <- simulate_RL (n = ncon_Mill, est_m = 0.01, est_sd = 0.15, plotting, min0=TRUE)

#b0
Mill_b0_pat <- simulate_RL (n = npat_Mill, est_m = 0.86, est_sd = 0.30, plotting, min0=FALSE) #-20 to 20
Mill_b0_con <- simulate_RL (n = ncon_Mill, est_m = 0.86, est_sd = 0.36, plotting, min0=FALSE)  

#b1
Mill_b1_pat <- simulate_RL (n = npat_Mill, est_m = 2.22, est_sd = 1.31, plotting, min0=FALSE) #-20 to 20
Mill_b1_con <- simulate_RL (n = ncon_Mill, est_m = 2.60, est_sd = 1.37, plotting, min0=FALSE)

#w1
Mill_w1_pat <- simulate_RL (n = npat_Mill, est_m = 0.32, est_sd = 0.10, plotting, min0=TRUE) #0.001 to 0.999
Mill_w1_con <- simulate_RL (n = ncon_Mill, est_m = 0.28, est_sd = 0.10, plotting, min0=TRUE)

#w2
Mill_w2_pat <- simulate_RL (n = npat_Mill, est_m = 0.21, est_sd = 0.09, plotting, min0=TRUE) #0.001 to 0.999
Mill_w2_con <- simulate_RL (n = ncon_Mill, est_m = 0.23, est_sd = 0.08, plotting, min0=TRUE)

#learning rate
Mill_alpha_pat <- simulate_RL (n = npat_Mill, est_m = 0.16, est_sd = 0.11, plotting, min0=TRUE) #0 to 1
Mill_alpha_con <- simulate_RL (n = ncon_Mill, est_m = 0.14, est_sd = 0.10, plotting, min0=TRUE)

#omega
Mill_omega_pat <- simulate_RL (n = npat_Mill, est_m = 1.84, est_sd = 0.32, plotting, min0=TRUE) #0.001 to 20
Mill_omega_con <- simulate_RL (n = ncon_Mill, est_m = 1.90, est_sd = 0.28, plotting, min0=TRUE)

Mill_params<-cbind(c(Mill_T_pat,Mill_T_con),c(Mill_b0_pat,Mill_b0_con),c(Mill_b1_pat,Mill_b1_con),c(Mill_w1_pat,Mill_w1_con),c(Mill_w2_pat,Mill_w2_con),c(Mill_alpha_pat,Mill_alpha_con),c(Mill_omega_pat,Mill_omega_con))
save(Mill_params,file='N:/Alex/metaRL/simulated_data/Mill_params')
```

Get Mukherjee parameters

```{r}
Mukherjee_data<-read.csv('N:/Alex/metaRL/data_from_papers/Filipowicz_data.csv')

npat_Mukherjee<-nrow(Mukherjee_data[Mukherjee_data$Group=='MDD' & Mukherjee_data$Condition=='Reward',])
ncon_Mukherjee<-nrow(Mukherjee_data[Mukherjee_data$Group=='Healthy Controls' & Mukherjee_data$Condition=='Reward',])
nsub_Mukherjee<-npat_Mukherjee+ncon_Mukherjee

#patients win
Mukherjee_alpha_f_win_pat<-Mukherjee_data$Alpha_F[Mukherjee_data$Group=='MDD' & Mukherjee_data$Condition=='Reward']
Mukherjee_beta_f_win_pat<-Mukherjee_data$Beta_F[Mukherjee_data$Group=='MDD' & Mukherjee_data$Condition=='Reward']
Mukherjee_beta_a_win_pat<-Mukherjee_data$Beta_A[Mukherjee_data$Group=='MDD' & Mukherjee_data$Condition=='Reward']
Mukherjee_persev_f_win_pat<-Mukherjee_data$Persev_F[Mukherjee_data$Group=='MDD' & Mukherjee_data$Condition=='Reward']
Mukherjee_persev_a_win_pat<-Mukherjee_data$Persev_A[Mukherjee_data$Group=='MDD' & Mukherjee_data$Condition=='Reward']
Mukherjee_bias_f_win_pat<-Mukherjee_data$Bias_F[Mukherjee_data$Group=='MDD' & Mukherjee_data$Condition=='Reward']
Mukherjee_bias_a_win_pat<-Mukherjee_data$Bias_A[Mukherjee_data$Group=='MDD' & Mukherjee_data$Condition=='Reward']

#patients loss
Mukherjee_alpha_f_loss_pat<-Mukherjee_data$Alpha_F[Mukherjee_data$Group=='MDD' & Mukherjee_data$Condition=='Punish']
Mukherjee_beta_f_loss_pat<-Mukherjee_data$Beta_F[Mukherjee_data$Group=='MDD' & Mukherjee_data$Condition=='Punish']
Mukherjee_beta_a_loss_pat<-Mukherjee_data$Beta_A[Mukherjee_data$Group=='MDD' & Mukherjee_data$Condition=='Punish']
Mukherjee_persev_f_loss_pat<-Mukherjee_data$Persev_F[Mukherjee_data$Group=='MDD' & Mukherjee_data$Condition=='Punish']
Mukherjee_persev_a_loss_pat<-Mukherjee_data$Persev_A[Mukherjee_data$Group=='MDD' & Mukherjee_data$Condition=='Punish']
Mukherjee_bias_f_loss_pat<-Mukherjee_data$Bias_F[Mukherjee_data$Group=='MDD' & Mukherjee_data$Condition=='Punish']
Mukherjee_bias_a_loss_pat<-Mukherjee_data$Bias_A[Mukherjee_data$Group=='MDD' & Mukherjee_data$Condition=='Punish']

#controls win
Mukherjee_alpha_f_win_con<-Mukherjee_data$Alpha_F[Mukherjee_data$Group=='Healthy Controls' & Mukherjee_data$Condition=='Reward']
Mukherjee_beta_f_win_con<-Mukherjee_data$Beta_F[Mukherjee_data$Group=='Healthy Controls' & Mukherjee_data$Condition=='Reward']
Mukherjee_beta_a_win_con<-Mukherjee_data$Beta_A[Mukherjee_data$Group=='Healthy Controls' & Mukherjee_data$Condition=='Reward']
Mukherjee_persev_f_win_con<-Mukherjee_data$Persev_F[Mukherjee_data$Group=='Healthy Controls' & Mukherjee_data$Condition=='Reward']
Mukherjee_persev_a_win_con<-Mukherjee_data$Persev_A[Mukherjee_data$Group=='Healthy Controls' & Mukherjee_data$Condition=='Reward']
Mukherjee_bias_f_win_con<-Mukherjee_data$Bias_F[Mukherjee_data$Group=='Healthy Controls' & Mukherjee_data$Condition=='Reward']
Mukherjee_bias_a_win_con<-Mukherjee_data$Bias_A[Mukherjee_data$Group=='Healthy Controls' & Mukherjee_data$Condition=='Reward']

#controls loss
Mukherjee_alpha_f_loss_con<-Mukherjee_data$Alpha_F[Mukherjee_data$Group=='Healthy Controls' & Mukherjee_data$Condition=='Punish']
Mukherjee_beta_f_loss_con<-Mukherjee_data$Beta_F[Mukherjee_data$Group=='Healthy Controls' & Mukherjee_data$Condition=='Punish']
Mukherjee_beta_a_loss_con<-Mukherjee_data$Beta_A[Mukherjee_data$Group=='Healthy Controls' & Mukherjee_data$Condition=='Punish']
Mukherjee_persev_f_loss_con<-Mukherjee_data$Persev_F[Mukherjee_data$Group=='Healthy Controls' & Mukherjee_data$Condition=='Punish']
Mukherjee_persev_a_loss_con<-Mukherjee_data$Persev_A[Mukherjee_data$Group=='Healthy Controls' & Mukherjee_data$Condition=='Punish']
Mukherjee_bias_f_loss_con<-Mukherjee_data$Bias_F[Mukherjee_data$Group=='Healthy Controls' & Mukherjee_data$Condition=='Punish']
Mukherjee_bias_a_loss_con<-Mukherjee_data$Bias_A[Mukherjee_data$Group=='Healthy Controls' & Mukherjee_data$Condition=='Punish']

Mukherjee_params<-cbind(c(Mukherjee_alpha_f_win_pat,Mukherjee_alpha_f_win_con),
                        c(Mukherjee_alpha_f_loss_pat,Mukherjee_alpha_f_loss_con),
                        c(Mukherjee_beta_f_win_pat,Mukherjee_beta_f_win_con),
                        c(Mukherjee_beta_f_loss_pat,Mukherjee_beta_f_loss_con),
                        c(Mukherjee_beta_a_win_pat,Mukherjee_beta_a_win_con),
                        c(Mukherjee_beta_a_loss_pat,Mukherjee_beta_a_loss_con),
                        c(Mukherjee_persev_f_win_pat,Mukherjee_persev_f_win_con),
                        c(Mukherjee_persev_f_loss_pat,Mukherjee_persev_f_loss_con),
                        c(Mukherjee_persev_a_win_pat,Mukherjee_persev_a_win_con),
                        c(Mukherjee_persev_a_loss_pat,Mukherjee_persev_a_loss_con),
                        c(Mukherjee_bias_f_win_pat,Mukherjee_bias_f_win_con),
                        c(Mukherjee_bias_f_loss_pat,Mukherjee_bias_f_loss_con),
                        c(Mukherjee_bias_a_win_pat,Mukherjee_bias_a_win_con),
                        c(Mukherjee_bias_a_loss_pat,Mukherjee_bias_a_loss_con))
save(Mukherjee_params,file='N:/Alex/metaRL/simulated_data/Mukherjee_params')
```

